PM Mungbean meta-analysis

### 2019-06-20 01_Meta-analysis_experiments.Rmd
Moved code chunck to experiment description chapter

>>>>

## Experimental locations
```{r Experiment_locations}

experiment_sites <- data.frame(
   location = c("Hermitage", "Kingaroy research station","Gatton", "Emerald Agricultural College"),
   lat = c(-28.215 ,-26.58,-27.56,-23.54),
   lon = c(152.1003,151.83,152.32,148.19)
)

 leaflet() %>%
    addProviderTiles("Esri.WorldTopoMap") %>%
    addMarkers(lng = experiment_sites$lon, lat = experiment_sites$lat)
# head(silo_gatton_Tmax)

```
